\documentclass[12pt,letterpaper,oneside]{book}
\usepackage{../../afitStyleFiles/afitThesis}
\usepackage[nolist]{acronym}
\usepackage{todo}
\usepackage{tabu}
\usepackage{makecell}
\renewcommand\theadfont{\bfseries}
\graphicspath{{../../Figures/}}
\input{../Preamble/myFigures}
\input{../Preamble/myTables}
\usepackage[outdir=./]{epstopdf}

\begin{document}
	\begin{acronym}
		\acro {BLE} {Bluetooth Low Energy}
		\acro {SIG} {Special Interest Group}
		\acro {BR/EDR} {Basic Rate/Enhanced Data Rate}
		\acro {IoT} {internet of things}
		\acro {CI} {critical infrastructure}
		\acro {WSN} {Wireless Sensor Network}
		\acro {ATT} {Attribute Protocol}
		\acro {GATT} {Generic Attribute Profile}
		\acro {SM} {Security Manager}
		\acro {LTK} {Long Term Key}
		\acro {CSRK} {Connection Signature Resolving Key}
		\acro {IRK} {Identity Resolving Key}
		\acro {AES} {Advanced Encryption Standard}
		\acro {TK} {Temporary Key}
		\acro {STK} {Short-Term Key}
		\acro {ECDH} {Elliptic Curve Diffie Hellman}
		\acro {CE} {Connection Events}
		\acro {CRC} {Cyclic Redundancy Check}
		\acro {SCA} {sleep clock accuracy}
		\acro {RSSI} {Received Signal Strength Indicator}
		\acro {MAC} {Media Access Control}
		\acro {CRM} {Customer Relationship Management}
		\acro {SSID} {Service Set Identifiers}
		\acro {AP} {access point}
		\acro {COTS} {commercial off-the-shelf}
		\acro {CITIoT} {Classification, Identification, an Tracking of \ac{IoT}}
		\acro {MIoTL} {Mitigation of \ac{IoT} Leakage}
		\acro {SHAA} {Smart Home Automation Architecture}
	\end{acronym}
\mainmatter
	\chapter{Introduction}
	
		\section{Background}
		In recent years, smart home devices have become one of the most popular categories in the \ac{IoT} accounting for \$3.5 billion of a \$292 billion industry; over 29 million smart home devices are expected to ship in 2017, a 63 percent increase over 2016 \cite{consumerTech}. Informed purchasing is of primary concern as retailers provide smart home devices from manufacturers with little scrutiny in regards to device security or known vulnerabilities. These devices are relatively inexpensive and can be purchased, shipped, and integrated into a smart home in days; the barrier of entry is very low. As smart home technologies become more popular and easier to obtain, the increased prevalence of \ac{IoT} devices in the home necessitates the need for investigation into what kind of privacy information these devices inadvertently broadcast, what vulnerabilities exist, and how privacy leakage can be used against consumers.
		\todo{get new numbers for 2018 or actual numbers from 2017}
		
		\section{Problem Statement}
		Wi-Fi and \ac{BLE} are two protocols increasingly used in a range of \ac{IoT} devices such as security cameras, locks, medical devices, sensors, and a myriad of other devices. These protocols broadcast some information in the clear that anyone with a properly-tuned receiver can observe. Smart home devices using these technologies are at risk of leaking privacy data that an outside observer may use to infer facts about the smart home such as what devices are in the home and when is the user away. Foremost, smart home owners must be informed of potential physical security implications \ac{IoT} devices can introduce to their home. For example, installing a vulnerable \ac{BLE} lock can allow attackers unfettered access to the home. Consumers must also have a way to defend against privacy leakage in their homes and mitigation methods need to be developed. The problem statement this thesis answers is what kind of privacy data do smart home devices leak, how can an attacker exploit this leakage to gain physical access to a home, and are there ways to defend against these vulnerabilities?
		
		\section{Research Goals}
		This work attempts to investigate this problem of data leakage in smart home devices and to see what extent information is sent in the clear by devices. It observes what reconnaissance methods an eavesdropper can use to collect wireless traffic from devices without being connected to the smart home environment and what kind of knowledge can be inferred about the smart home and its users. After collecting data from devices, this research attempts to analyze what physical security ramifications this leakage introduces. It also attempts to defend against data leakage by mitigating these findings.
		
		\section{Hypothesis}
		This research hypothesizes that \ac{IoT} device leakage can be used to classify smart home devices, track whether a user is in the home or not, and identify events, such as when a door is opened or when a light is turned on, with a success rate of above 90\% and a false positive rate of less than 10\%. It also theorizes that impact of data leakage can be mitigated using existing methods and techniques at a success rate of above 90\%.
		
		\section{Approach}
		To represent a realistic smart home environment, a voice activated digital assistant and \ac{IoT} architecture is developed by integrating a variety of \ac{COTS} Wi-Fi and \ac{BLE} devices with Apple's home automation application, HomeKit. Furthermore, a device classifier and pattern-of-life analysis tool is created to analyze data leakage within the smart home architecture attempting to classify devices, identify events, and track whether a user is in the home or away. Findings are synthesized to observe physical security implications and ways to mitigate vulnerabilities.
		
		\section{Assumptions/Limitations}
		The following assumptions/limitations are understood when designing and executing for the \ac{CITIoT} tool:
		\begin{itemize}
			\item The devices selected and smart home architecture are representative of a realistic environment.
			\item Wi-Fi device categories are limited to the following: outlet, sensor, and camera.
			\item All Wi-Fi devices must be compatible with the Homebridge server.
		\end{itemize}
		
		\section{Contributions}
		This thesis contributes to the field of \ac{IoT} security, specifically privacy within a smart home through four principal contributions:
		\begin{itemize}
			\item \textbf{Smart home architecture.} To analyze \ac{IoT} data leakage in the wild, a realistic \acf{SHAA} is provided that integrates Wi-Fi and \ac{BLE} \ac{COTS} devices with Apple's home automation application, HomeKit.
			\item \textbf{Vulnerability Analysis.} This work explains how an eavesdropper can use device vulnerabilities, characteristic data exchanges, and packet sizes to create a classifier able to identify components and events within the smart home environment.
			\item \textbf{\acf{CITIoT}.} It presents a tool that demonstrates four capabilities enabled by data leakage: network mapping, device classification, event identification, and user tracking.
			\item \textbf{Synthesis.} It stresses the importance of smart home operational security by demonstrating how \ac{CITIoT} can be used to gain physical access to a smart home when a user is away.
		\end{itemize}
		
		\section{Thesis Overview}
		This thesis document is arranged in six chapters. Chapter 2 provides a brief summary of relevant wireless protocols, an outline of open-source security analysis tools used, and other relevant research. Chapter 3 presents the system design details, smart home architecture, and mitigation techniques developed to analyze, exploit,and prevent smart home privacy leakage. The experiment methodology and the analysis of results are presented in Chapters 4 and 5 respectively, while Chapter 6 summarizes the research and discusses opportunities for future work in this domain.
		
		
	\todos
\backmatter
	\singlespace
	\bibliographystyle{plain}
	\bibliography{../Back/myReferences} 
	\clearpage

\end{document}

